---
title: "BacTMAP"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bactMAP)
library(R.matlab)
library(ggplot2)
library(mvtnorm)
library(shotGroups)
```

## BacTMAP - Bacteria Tool for Microscopy Analysis & Plotting

This R package is developed for easy processing, analysis & plotting of segmentation & fluorescence data from multiple popular bacterial (phase-contrast) segmentation tools, like Oufti, MicrobeJ & Morphometrics. The data can be combined with the raw data or spot detection data from other programs.

## Importing data

All importing functions start with **extr.**. See help(bactMAP::extr.all) in the package documentation for a full overview of all import functions.

For example, use **extr.Oufti(rawdatafile, pixels2um)** to load segmentation & spot detection data generated with Oufti, where *rawdatafile* is the location of the .MAT file containing the Oufti output, and *pixels2um* is the conversion factor from the pixels in the data to actual micrometers. This can differ per lab, dependent on the objective and the camera used, therefore you can add your own conversion factor using **addPixels2um()**:

```{r}
#Add your own pixels to um conversion factor:


oufti_example <- system.file("extdata", "oufti_sp_gfpsmc.MAT", package = "bactMAP")
extr.Oufti(oufti_example, "100x_LeicaVeening")


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
